Fusion of Mass Spectrometry and Raman Spectroscopy Data Case Study 2

### 2024-06-11 dev/dev_paracetamol.Rmd
Update dev_paracetamol.Rmd

@@

@@

raman_files <- list.files(raman_dir, pattern = ".asc", full.names = TRUE)
```

@@

@@

@@

# Raman quantification

@@

```{r}

>>>>

ms_dir_extra <- paste0(main_dir, "/ms/extra/mzml")

@@

ms_files_extra <- list.files(ms_dir_extra, pattern = ".mzML", full.names = TRUE)

@@

raman_dir_extra <- paste0(main_dir, "/raman/extra")

raman_files <- list.files(raman_dir, pattern = ".asc", full.names = TRUE)

raman_files_extra <- list.files(raman_dir_extra, pattern = ".asc", full.names = TRUE)
```

@@

```{r raman-spectra}
raman$get_spectra()[1:10, ]
```

@@

```{r extra-data, include=FALSE}
ms_extra <- MassSpecEngine$new(files = ms_files_extra[c(5:40, 49:60)])

ms_extra$add_replicate_names(
  c(
    rep("fiz_e01", 3),
    rep("fiz_e02", 3),
    rep("fiz_e03", 3),
    rep("fiz_e04", 3),
    rep("fiz_e05", 3),
    rep("fiz_e06", 3),
    rep("fiz_e07", 3),
    rep("fiz_e08", 3),
    rep("fiz_e09", 3),
    rep("fiz_e10", 3),
    rep("fiz_e11", 3),
    rep("fiz_e12", 3),
    rep("blank", 12)
  )
)

ms_extra$add_blank_names(rep("blank", 48))

ms_extra$load_spectra()

ms_extra$add_settings(ms_workflow_settings)

ms_extra$run_workflow()

ms_extra$plot_spectra()
```

@@

# Quantification with Raman

@@

```{r, include=FALSE, eval=FALSE}
